---
title: "Crop diversity influences disease suppression in soils"
author: "Ariane L. Peralta, Yanmei Sun, Marshall McDaniel, Jay T. Lennon" - acknowledge Mario Muscarella for analyses help!
date: "Last updated on `r format(Sys.time(), '%d %B, %Y')`"
header-includes:
  - \usepackage{array}
  - \usepackage{graphics}
output: 
  pdf_document:
  fig_caption: true
---

Project Description: 

```{r}
#Crop Diversity - redo stats to double check for publication

#based on 0.03 taxonomy of 16S rRNA Illumina sequences
#(1) Run diversity analyses (Hdiversity, richness, evenness)
#-need to re-run
#(2) PERMANOVA -completed for treatment and for soil factors
#(3) PCoA 
#(4) Mantel test to compare total bacterial and PHLD communities (16S rRNA related to plant path suppression?) - we ran and no relationship 

#Functional Gene Analysis (disease suppression)
#(1) PRND gene qPCR ANOVA and boxplot
#(2) PHLD gene TRFLP -PERMANOVA and PCoA 
```

# Initial Setup
```{r}
rm(list=ls())
setwd("~/GitHub/CropDiversity/analyses")
se <- function(x, ...){sd(x, na.rm = TRUE)/sqrt(length(na.omit(x)))}
ci <- function(x, ...){1.96 * sd(x,na.rm = TRUE)}

# Code Dependencies
source("../bin/DiversityFunctions.R")
source("../bin/MothurTools.R")
require("vegan")
require("nlme")
require("reshape")
#require("BiodiversityR")
# require("ecodist")
require("ggplot2")
require("ade4")
require("png")
require ("agricolae")
```

# Environmental Data
```{r}
# Import Environmental Data
design.in <- read.csv("../data/BDsoil_exptdesign.csv", row.names = 1)

# ID S and W treatments
SnW <- rownames(design.in[which(design.in$rotation == "S" | 
                                  design.in$rotation == "W"), ])

# Remove S and W treatments
design <- design.in[-(which(rownames(design.in) %in% SnW)), ]
design <- droplevels(design)

# Define Treatments ###check order of treatments
treatments <- factor(design$rotation, levels = c("fallow", "CSW-2cov", 
                     "CSW-1cov", "CSW", "CS", "C-1cov", "C"))

all.equal(as.character(design$rotation), as.character(treatments))
```

# Microbial Data
```{r}
# Import OTU data
# Import Raw Data
BDdata.in <- read.otu("../data/BD.shared")

# Remove Mock Community, Blank and Undetermined
BDdata.in2 <- BDdata.in[grepl("BD[0-9][0-9]", rownames(BDdata.in)), ]

# Remove S and W Treatments
SnW2 <- gsub("-", "", SnW)
BDdata.in2 <- BDdata.in2[-(which(rownames(BDdata.in2) %in% SnW2)), ]

# Remove OTUs with less than two occurences across all sites
BDdata <- BDdata.in2[, which(colSums(BDdata.in2) >= 2)]

# Make Presence Absence Matrix
BDdataPA <- (BDdata > 0) * 1

# Make Relative Abundence Matrices
BDdataREL <- BDdata
for(i in 1:dim(BDdata)[1]){
  BDdataREL[i,] <- BDdata[i,]/sum(BDdata[i,])
}

# Log Transform Relative Abundances
BDdataREL.log <- decostand(BDdataREL, method="log")

# Import Taxonomy File
BD.tax <- read.tax(taxonomy = "../data/BD.0.03.cons.taxonomy", format = "rdp", 
                   tax.levels = 6, col.tax = 3)
```

# Plant Data
```{r}
BDveg.in <- read.csv("../data/BDveg.csv", row.names = 1)

# Remove S and W Treatments
BDveg <- BDveg.in[-(which(rownames(BDveg.in) %in% SnW)), ]

# plant data as discrete and continuous biomass data: rotation	crop_numb	covercrop_g	weeds_g	crop_g	biomass_total	covercrop_prop	weeds_prop	crop_prop
```

# Diversity Metrics - Hypothesis Testing
```{r}
# Rarefy Abundances (min abundance is 267,170. We are sampling to 200,000)
min(rowSums(BDdata))
BDdata.r <- rrarefy(BDdata, 200000)

# Fisher's Alpha
fisher <- fisher.alpha(BDdata.r)
fisher

# Species Richness
richness <- rowSums((BDdata.r >= 1))

# Shannon Diversity (my function gets the same answer)
shannon <- diversity(BDdata.r, "shannon")

# Simpson's Evenness
simp.even <- apply(BDdata.r, 1, simp_even)

# Alternative way for evenness (note: uses D = sum[p_i^2] not corrected D)
#simp.even2 <- diversity(BDdata.r, "invsimpson")/specnumber(BDdata.r)

#Pielou’s evenness
J <- shannon/log(specnumber(BDdata.r[,-c(1:1)]))

#combined richness, diversity, evenness
BD.DIVsoilmicrobes <- cbind(design,richness,shannon,simp.even,J)
write.table(BD.DIVsoilmicrobes, file="BD.DIVsoilmicrobes.csv", sep=",", col.names=NA)


# Hypothesis Testing
# First Check the order
length(design$rotation) == length(fisher)
all.equal(gsub("-", "", rownames(design)), names(fisher))

fisher.lm <- lme(fisher ~ rotation, random = ~1|block, data = design)
anova(fisher.lm)

richness.lm <- lme(richness ~ rotation, random = ~1|block, data = design)
anova(richness.lm)

evenness.lm <- lme(simp.even ~ rotation, random = ~1|block, data = design)
anova(evenness.lm)

shannon.lm <- lme(shannon ~ rotation, random = ~1|block, data = design)
anova(shannon.lm)

library(agricolae)
summary(shannon.lm)
shannon.lm2 <- lm(shannon ~ rotation, data = BD.DIVsoilmicrobes)
HSD <- HSD.test(shannon.lm2,"rotation", console=TRUE)
```
#boxplot shannon diversity #still need to add postdoc labels on graph
```{r}
p <- ggplot(BD.DIVsoilmicrobes, aes(rotation,shannon))
p + geom_boxplot() + theme_bw()
p + geom_boxplot() + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor =     element_blank(), axis.line = element_line(colour = "black")) +   
  theme(axis.title=element_text(vjust=1,size=16,face="bold"), axis.text=element_text(size=14), 
  axis.text.x = element_text(vjust=0.65, hjust=0.5, angle=30, size=14), panel.border =   
  element_rect(colour = "black",size=1.25)) + theme(axis.ticks.length=unit(0.3,"cm")) + 
  xlab("Crop Diversity") + ylab("Shannon Diversity Index (H')") + 
  scale_x_discrete(breaks=c("fallow", "CSW-2cov", "CSW-1cov", "CSW", "CS", "C-1cov", "C"),   
  labels=c("fallow", "CSW_2cov", "CSW_1cov", "CSW", "CS","C_1cov", "mC"))

ggsave("../figures/shannonRplot.pdf", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=300, limitsize=TRUE)
```

#boxplot prnD disease suppression gene abundance - #still need to add postdoc labels on graph
```{r}
data.prnd <- read.csv("../data/PRND gene_NoSW.csv", header=TRUE)

prnd.lm <- lme(copies ~ Rotation, random = ~1|Block, data = data.prnd)
anova(prnd.lm)

library(agricolae)
prnd.lm2 <- lm(copies~Rotation,data=data.prnd)
summary(prnd.lm2)
HSD <- HSD.test(prnd.lm2,"Rotation", console=TRUE)

p <- ggplot(data.prnd, aes(Rotation,copies))
p + geom_boxplot() + theme_bw()
p + geom_boxplot() + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) +theme(axis.title=element_text(vjust=1,size=16,face="bold"), axis.text=element_text(size=14), axis.text.x = element_text(vjust=0.65, hjust=0.5, angle=30, size=14), panel.border = element_rect(colour = "black",size=1.25)) + theme(axis.ticks.length=unit(0.3,"cm")) + xlab("Crop Diversity") + ylab("prnD genes/g soil\n(log copy number)") +scale_x_discrete(breaks=c("fallow", "CSW-2cov", "CSW-1cov", "CSW", "CS", "C-1cov", "C"), labels=c("fallow", "CSW_2cov", "CSW_1cov", "CSW", "CS","C_1cov", "mC"))

ggsave("../figures/prnDabundanceRplot.pdf", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=300, limitsize=TRUE)

reg <- lm(copies~crop+carbon+moisture, data=data.prnd)
summary(reg)

```

# Simple Hypothesis Testing - 
```{r}
# Check that Bac and Plant data have same structure as design
row.names(BDdataREL) == row.names(design)

#PERMANOVA on rotation effect - no S and W
new.data <-cbind(design,BDdataREL)
adonis = adonis(new.data[,-c(1:15)] ~ rotation+block, method = "bray", data = new.data, perm=1000)
adonis
```
# Microbial Ordinations

## Principal Coordinates Ordination
```{r}
# TEST with original labels
# Create Distance Matrix
sampleREL.dist <- vegdist(BDdataREL, method="bray")

# Principal Coordinates Analysis
BD_pcoa <- cmdscale(sampleREL.dist, k=3, eig=TRUE, add=FALSE)
  # Classical (Metric) Multidimensional Scaling; returns PCoA coordinates
  # eig=TRUE returns eigenvalues; k = # of dimensions to calculate

explainvar1 <- round(BD_pcoa$eig[1] / sum(BD_pcoa$eig), 3) * 100
explainvar2 <- round(BD_pcoa$eig[2] / sum(BD_pcoa$eig), 3) * 100
sum.eig <- sum(explainvar1, explainvar2)

points <- cbind(as.data.frame(BD_pcoa$points), design$rotation)
L.centroids <- melt(points, id="design$rotation", measure.vars = c("V1", "V2"))
centroids <- cast(L.centroids, variable ~ design$rotation, mean)
centroids.se <- cast(L.centroids, variable ~ design$rotation, se)
centroids.sd <- cast(L.centroids, variable ~ design$rotation, sd)

cent.dataframe <- t(data.frame(rbind(centroids[1,-1], centroids[2,-1],
                             centroids.sd[1,-1],centroids.sd[2,-1])))
colnames(cent.dataframe) <- c("V1", "V2", "V1e", "V2e")
cent.treats <- rownames(cent.dataframe)

explainvar1 #Include in PCoA 1 axis label 29.3%
explainvar2 #Include in PCoA 2 axis label 14.0%
                                        
df <- as.data.frame(cent.dataframe)
p <- ggplot(df, aes(x=V1, y=V2, colour=cent.treats)) + theme_bw() 
p + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + 
theme(panel.background = element_blank()) + 
  geom_errorbarh(aes(xmax=V1+V1e, xmin=V1-V1e, height=0.01), colour="black") +    
  geom_errorbar(aes(ymax=V2+V2e, ymin=V2-V2e, width=0.01), colour="black") + 
  geom_point(size=5) 

```

```{r}
# Create Distance Matrix
sampleREL.dist <- vegdist(BDdataREL, method="bray")

# Principal Coordinates Analysis
BD_pcoa <- cmdscale(sampleREL.dist, k=3, eig=TRUE, add=FALSE)
  # Classical (Metric) Multidimensional Scaling; returns PCoA coordinates
  # eig=TRUE returns eigenvalues; k = # of dimensions to calculate

explainvar1 <- round(BD_pcoa$eig[1] / sum(BD_pcoa$eig), 3) * 100
explainvar2 <- round(BD_pcoa$eig[2] / sum(BD_pcoa$eig), 3) * 100
sum.eig <- sum(explainvar1, explainvar2)
```

# Plot
```{r}
points <- cbind(as.data.frame(BD_pcoa$points), treatments)
L.centroids <- melt(points, id="treatments", measure.vars = c("V1", "V2"))
centroids <- cast(L.centroids, variable ~ treatments, mean)
centroids.se <- cast(L.centroids, variable ~ treatments, se)
centroids.sd <- cast(L.centroids, variable ~ treatments, sd)

cent.dataframe <- t(data.frame(rbind(centroids[1,-1], centroids[2,-1],
                             centroids.sd[1,-1],centroids.sd[2,-1])))
colnames(cent.dataframe) <- c("V1", "V2", "V1e", "V2e")
cent.treats <- rownames(cent.dataframe)

explainvar1 #Include in PCoA 1 axis label 29.3%
explainvar2 #Include in PCoA 2 axis label 14.0%
                                        
df <- as.data.frame(cent.dataframe)
p <- ggplot(df, aes(x=V1, y=V2, colour=cent.treats)) + theme_bw() 
p + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + 
theme(panel.background = element_blank()) + 
  geom_errorbarh(aes(xmax=V1+V1e, xmin=V1-V1e, height=0.01), colour="black") +    
  geom_errorbar(aes(ymax=V2+V2e, ymin=V2-V2e, width=0.01), colour="black") + 
  geom_point(size=5) +
  scale_colour_manual(labels = c("mC", "C_1cov", "CS", "CSW", "CSW_1cov", "CSW_2cov", "fallow"),   values = c("#FFFFCC", "#FFFF00", "#FF9933", "#66CC00", "#339900", "#336633", "#00CCFF")) +
  geom_point(shape=1, size = 5,colour = "black") +
theme(axis.title=element_text(size=18), axis.text=element_text(size=14), axis.text.x   = element_text(size=14), panel.border = element_rect(colour = "black",size=1.25)) + 
  theme(axis.ticks.length=unit(0.3,"cm")) + 
  xlab("PCoA 1 (29.3%)") + ylab("PCoA 2 (14.0%)") + 
  labs(color = "Crop diversity") +
  guides(colour = guide_legend(override.aes = list(pch=21, size = 4, colour="black",    
  fill=c("#FFFFCC", "#FFFF00", "#FF9933", "#66CC00", "#339900", "#336633", "#00CCFF")))) 

ggsave("../figures/16SrRNA_BCC_Rplot.pdf", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=300, limitsize=TRUE)



```
#PERMANOVA on soil factors - no S and W
#check for correlations among soil factors
#drop Total.N NA value
```{r}
new.data <- new.data[complete.cases(new.data),]
soil.factors <- new.data[,7:15]
cor(soil.factors)

#in soil model, include GWC, Total.C, ammonium, nitrate, pH, sand; note: GWC correlated to texture and Total.C, but included anyway

adonis = adonis(new.data[,-c(1:15)] ~ GWC + Total.C + Total.N + NH4 + NO3 + pHH2O + Clay + Silt + Sand, method = "bray", data = new.data, perm=1000)
adonis
# Terms added sequentially (first to last)

adonis = adonis(new.data[,-c(1:15)] ~ Sand + GWC + Total.C + Total.N + NH4 + NO3 + pHH2O + Clay + Silt, method = "bray", data = new.data, perm=1000)
adonis
# Terms added sequentially (first to last)

adonis = adonis(new.data[,-c(1:15)] ~ Silt + Sand  + GWC + Total.C + Total.N + NH4 + NO3 + pHH2O + Clay, method = "bray", data = new.data, perm=1000)
adonis
# Terms added sequentially (first to last)

adonis = adonis(new.data[,-c(1:15)] ~ Clay + Silt + Sand  + GWC + Total.C + Total.N + NH4 + NO3 + pHH2O, method = "bray", data = new.data, perm=1000)
adonis
# Terms added sequentially (first to last)

adonis = adonis(new.data[,-c(1:15)] ~ pHH2O + Clay + Silt + Sand  + GWC + Total.C + Total.N + NH4 + NO3, method = "bray", data = new.data, perm=1000)
adonis
# Terms added sequentially (first to last)

adonis = adonis(new.data[,-c(1:15)] ~ NO3 + pHH2O + Clay + Silt + Sand  + GWC + Total.C + Total.N + NH4, method = "bray", data = new.data, perm=1000)
adonis
# Terms added sequentially (first to last)

adonis = adonis(new.data[,-c(1:15)] ~  NH4 +NO3 + pHH2O + Clay + Silt + Sand  + GWC + Total.C + Total.N, method = "bray", data = new.data, perm=1000)
adonis
# Terms added sequentially (first to last)

adonis = adonis(new.data[,-c(1:15)] ~  Total.N + NH4 +NO3 + pHH2O + Clay + Silt + Sand  + GWC + Total.C, method = "bray", data = new.data, perm=1000)
adonis
# Terms added sequentially (first to last)

adonis = adonis(new.data[,-c(1:15)] ~ Total.C +  Total.N + NH4 +NO3 + pHH2O + Clay + Silt + Sand  + GWC, method = "bray", data = new.data, perm=1000)
adonis
# Terms added sequentially (first to last)
```

#PERMANOVA associated with soil biology
```{r}
#Import soil biology - PMN, POXC data
soilbio <- read.csv("../data/BDsoilbio.csv", row.names = 1)
soil.bio.microbes <- cbind(soilbio,BDdataREL)

adonis = adonis(soil.bio.microbes[,-c(1:6)] ~ POXC +  PMC + PMN, method = "bray", data = soil.bio.microbes, perm=1000)
adonis

adonis = adonis(soil.bio.microbes[,-c(1:6)] ~ PMN + POXC +  PMC, method = "bray", data = soil.bio.microbes, perm=1000)
adonis

adonis = adonis(soil.bio.microbes[,-c(1:6)] ~ PMC + PMN + POXC, method = "bray", data = soil.bio.microbes, perm=1000)
adonis
```

#PERMANOVA associated with plant factors
```{r}
plant.microbes <- cbind(BDveg,BDdataREL)

adonis = adonis(plant.microbes[,-c(1:13)] ~   crop_numb + covercrop_g + weeds_g + crop_g , method = "bray", data = plant.microbes, perm=1000)
adonis

adonis = adonis(plant.microbes[,-c(1:13)] ~  crop_g + crop_numb + covercrop_g + weeds_g, method = "bray", data = plant.microbes, perm=1000)
adonis

adonis = adonis(plant.microbes[,-c(1:13)] ~ weeds_g + crop_g + crop_numb + covercrop_g, method = "bray", data = plant.microbes, perm=1000)
adonis

adonis = adonis(plant.microbes[,-c(1:13)] ~ covercrop_g + weeds_g + crop_g + crop_numb, method = "bray", data = plant.microbes, perm=1000)
adonis
```

#PERMANOVA on PHLD gene TRFLP - PPS TRFLP - need to check
```{r}
phld.in <- read.csv("../data/TRFLP_Original.csv", row.names = 1)

# ID S and W treatments
SnW <- rownames(phld.in[which(phld.in$rotation == "S" | 
                                  phld.in$rotation == "W"), ])

# Remove S and W treatments
phld <- phld.in[-(which(rownames(phld.in) %in% SnW)), ]
phld <- droplevels(phld)
str(phld)

phld.test <- data.frame(lapply(phld[,-c(1:7)], as.numeric))
str(phld.test)

# Make Relative Abundance Matrices

phldREL <- phld.test
for(i in 1:dim(phld.test)[1]){
  phldREL[i,] <- phld.test[i,]/sum(phld.test[i,], na.rm=T)
}

new.phldREL <-cbind(phld[,c(1:7)],phldREL)
str(new.phldREL)

###remove NA's from data set
library(tidyr)
new.phldREL2 <- new.phldREL %>% drop_na()
str(new.phldREL2)

#PERMANOVA on rotation effect - no S and W
adonis = adonis(new.phldREL2[,-c(1:7)] ~ rotation+block, method = "bray", data = new.phldREL2, perm=1000)
adonis

# Define Treatments ###check order of treatments
treatments <- factor(new.phldREL2$rotation, levels = c("fallow", "CSW-2cov", 
                     "CSW-1cov", "CSW", "CS", "C-1cov", "C")) 
all.equal(as.character(new.phldREL2$rotation), as.character(treatments))

```

#Ordination of PHLD disease suppression functional gene - dropped S and W
## Principal Coordinates Ordination
```{r}
# TEST with original labels
# Create Distance Matrix
phldREL3 <- new.phldREL2[,-c(1:7)]
design <- new.phldREL2[,c(1:7)]
sampleREL.dist <- vegdist(phldREL3, method="bray")

# Principal Coordinates Analysis
BD_pcoa <- cmdscale(sampleREL.dist, k=3, eig=TRUE, add=FALSE)
  # Classical (Metric) Multidimensional Scaling; returns PCoA coordinates
  # eig=TRUE returns eigenvalues; k = # of dimensions to calculate

explainvar1 <- round(BD_pcoa$eig[1] / sum(BD_pcoa$eig), 3) * 100
explainvar2 <- round(BD_pcoa$eig[2] / sum(BD_pcoa$eig), 3) * 100
sum.eig <- sum(explainvar1, explainvar2)

all.equal(rownames(design), rownames(BD_pcoa$points))

points <- cbind(as.data.frame(BD_pcoa$points), design$rotation)
L.centroids <- melt(points, id="design$rotation", measure.vars = c("V1", "V2"))
centroids <- cast(L.centroids, variable ~ design$rotation, mean)
centroids.se <- cast(L.centroids, variable ~ design$rotation, se)
centroids.sd <- cast(L.centroids, variable ~ design$rotation, sd)

cent.dataframe <- t(data.frame(rbind(centroids[1,-1], centroids[2,-1],
                             centroids.sd[1,-1],centroids.sd[2,-1])))
colnames(cent.dataframe) <- c("V1", "V2", "V1e", "V2e")
cent.treats <- rownames(cent.dataframe)

explainvar1 #Include in PCoA 1 axis label 29.3%
explainvar2 #Include in PCoA 2 axis label 14.0%
                                        
df <- as.data.frame(cent.dataframe)
p <- ggplot(df, aes(x=V1, y=V2, colour=cent.treats)) + theme_bw() 
p + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + 
theme(panel.background = element_blank()) + 
  geom_errorbarh(aes(xmax=V1+V1e, xmin=V1-V1e, height=0.01), colour="black") +    
  geom_errorbar(aes(ymax=V2+V2e, ymin=V2-V2e, width=0.01), colour="black") + 
  geom_point(size=5) 

```

```{r}
# UPDATE and fix color/labels
# Create Distance Matrix
sampleREL.dist <- vegdist(phldREL3, method="bray")

# Principal Coordinates Analysis
phld_pcoa <- cmdscale(sampleREL.dist,k=3,eig=TRUE,add=FALSE)
  # Classical (Metric) Multidimensional Scaling; returns PCoA coordinates
  # eig=TRUE returns eigenvalues; k = # of dimensions to calculate

explainvar1 <- round(phld_pcoa$eig[1]/sum(phld_pcoa$eig)*100,2)
explainvar2 <- round(phld_pcoa$eig[2]/sum(phld_pcoa$eig)*100,2)
explainvar3 <- round(phld_pcoa$eig[3]/sum(phld_pcoa$eig)*100,2)
explainvar1 #PCoA 1 (22.4%)
explainvar2 #PCoA 2 (20.6%)
explainvar3

sum.eig <- sum(explainvar1, explainvar2)
```

# Plot PPS TRFLP Ordination
```{r}
all.equal(as.character(treatments), as.character(design$rotation))

points <- cbind(as.data.frame(phld_pcoa$points), treatments)
L.centroids <- melt(points, id="treatments", measure.vars = c("V1", "V2"))
centroids <- cast(L.centroids, variable ~ treatments, mean)
centroids.se <- cast(L.centroids, variable ~ treatments, se)
centroids.sd <- cast(L.centroids, variable ~ treatments, sd)

cent.dataframe <- t(data.frame(rbind(centroids[1,-1], centroids[2,-1],
                             centroids.sd[1,-1],centroids.sd[2,-1])))
colnames(cent.dataframe) <- c("V1", "V2", "V1e", "V2e")
cent.treats <- rownames(cent.dataframe)

explainvar1 #Include in PCoA 1 axis label 29.3%
explainvar2 #Include in PCoA 2 axis label 14.0%
                                        
df <- as.data.frame(cent.dataframe)
p <- ggplot(df, aes(x=V1, y=V2, colour=cent.treats)) + theme_bw() 
p + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + 
theme(panel.background = element_blank()) + 
  geom_point(size=5) +
  geom_errorbarh(aes(xmax=V1+V1e, xmin=V1-V1e, height=0.01), colour="black") +    
  geom_errorbar(aes(ymax=V2+V2e, ymin=V2-V2e, width=0.01), colour="black") +
  scale_colour_manual(labels = c("mC", "C_1cov", "CS", "CSW", "CSW_1cov", "CSW_2cov", "fallow"),   values = c("#FFFFCC", "#FFFF00", "#FF9933", "#66CC00", "#339900", "#336633", "#00CCFF")) +
  geom_point(shape=1, size = 5,colour = "black") +
theme(axis.title=element_text(size=18), axis.text=element_text(size=14), axis.text.x   = element_text(size=14), panel.border = element_rect(colour = "black",size=1.25)) + 
  theme(axis.ticks.length=unit(0.3,"cm")) + 
  xlab("PCoA 1 (29.3%)") + ylab("PCoA 2 (14.0%)") + 
  labs(color = "Crop diversity") +
  guides(colour = guide_legend(override.aes = list(pch=21, size = 4, colour="black",    
  fill=c("#FFFFCC", "#FFFF00", "#FF9933", "#66CC00", "#339900", "#336633", "#00CCFF")))) 

ggsave("../figures/PHLD_Rplot.pdf", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=300, limitsize=TRUE)


####
points <- cbind(as.data.frame(phld_pcoa$points), treatments)
L.centroids <- melt(points, id="treatments", measure.vars = c("V1", "V2"))
centroids <- cast(L.centroids, variable ~ treatments, mean)
centroids.se <- cast(L.centroids, variable ~ treatments, se)
centroids.sd <- cast(L.centroids, variable ~ treatments, sd)

cent.dataframe2 <- t(data.frame(rbind(centroids[1,-1], centroids[2,-1],
                             centroids.sd[1,-1],centroids.sd[2,-1])))
colnames(cent.dataframe2) <- c("V1", "V2", "V1e", "V2e")
cent.treats <- rownames(cent.dataframe2)

df <- as.data.frame(cent.dataframe2)
p2 <- ggplot(df, aes(x=V1, y=V2, colour=cent.treats)) + theme_bw() 
p2 + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + theme(panel.background = element_blank()) + 
  geom_errorbarh(aes(xmax=V1+V1e, xmin=V1-V1e, height=0.001), colour="black") +    
  geom_errorbar(aes(ymax=V2+V2e, ymin=V2-V2e, width=0.001), colour="black") + 
  geom_point(size=6) +
  scale_colour_manual(labels = c("mC", "C_1cov", "CS", "CSW", "CSW_1cov", "CSW_2cov", "fallow"),   values = c("#FFFFCC", "#FFFF00", "#FF9933", "#66CC00", "#339900", "#336633", "#00CCFF")) +
  geom_point(shape=1, size = 6,colour = "black") +
theme(axis.title=element_text(size=18), axis.text=element_text(size=14), axis.text.x   = element_text(size=14), panel.border = element_rect(colour = "black",size=1.25)) + 
  theme(axis.ticks.length=unit(0.3,"cm")) + 
  xlab("PCoA 1 (29.3%)") + ylab("PCoA 2 (14.0%)") + 
  labs(color = "Crop diversity") +
  guides(colour = guide_legend(override.aes = list(pch=21, size = 6, colour="black",    
  fill=c("#FFFFCC", "#FFFF00", "#FF9933", "#66CC00", "#339900", "#336633", "#00CCFF")))) 

ggsave("../figures/PHLD_Rplot.pdf", plot=last_plot(), device=NULL, path=NULL, scale=1, width=NA, height=NA, dpi=300, limitsize=TRUE)

```


